---
title: "Healthcare Consultations by Provider Type"
format: 
  html:
    toc: TRUE
    number-sections: TRUE
execute:
  echo: FALSE
  warning: FALSE
  message: FALSE
---

```{r}

library(dplyr)
library(ggplot2)
library(readr)
library(knitr)

df <- read_csv("../data/sample_data.csv")

```

# Project Summary

This report analyses healthcare service utilisation across different provider types (GP, Nurse, Allied Health, Dentist).

Key findings include:

- GP services account for the highest number of consultations overall.
- Consultation patients vary across provider types over time.
- Difference are observed across population groups (age and gender).

These insights can support service planning and resource allocation decisions.

The chart shows that consultation patterns differ across age groups, with certain provider types being more prominent in specific age segments. This suggests potential differences in healthcare needs across the population.

```{r}

age_provider <- df |>
  group_by(age_group, provider_type) |>
  summarise(total_consultations = sum(n_consultations),
            .groups = "drop")

ggplot(age_provider,
       aes(x = age_group,
           y = total_consultations,
           fill = provider_type)
       ) +
  geom_col(position = "dodge") +
  labs(title = "Consultations by age group and provider type",
       x = "Age group",
       y = "Total consultations")
```

# Data Overview
```{r}

summary_tab <- df |>
  summarise(total_people = sum(n_people),
           total_consultations = sum(n_consultations),
           avg_consultations_per_ppl = round(total_consultations / total_people, 2)
  )

kable(summary_tab)

```

# Total Consultations by Provider Type
```{r}

summary_provider <- df |>
  group_by(provider_type) |>
  summarise(total_consultations = sum(n_consultations),
           .groups = "drop")

ggplot(summary_provider,
       aes(x = provider_type,
           y = total_consultations)
       ) +
  geom_col() +
  labs(title = "Total consultations by provider type",
       x = "Provider type",
       y = "Total consultations")

```

# Monthly Trend

```{r}

summary_monthly <- df |>
  group_by(month, provider_type) |>
  summarise(total_consultations = sum(n_consultations),
            .groups = "drop")

ggplot(summary_monthly,
       aes(x = month,
           y = total_consultations,
           group = provider_type,
           color = provider_type)
       ) +
  geom_line() +
  labs(title = "Monthly consultation trend by provider type",
       x = "Month",
       y = "Total consultations")
```
