---
title: "Healthcare Consultation Service Report"
output: 
  word_document:

<!--  use it when you have the docx,  reference_docx: ../templates/reference.docx -->
---

## Project Summary

This report summarises healthcare consultation service across provider types (GP, Nurse, Allied Health, Dentist).

Key findings include:

- GP services account for the highest number of consultations overall.
- Consultation patients vary across provider types over time.
- Difference are observed across population groups (age and gender).

```{r setup, include=FALSE}

library(dplyr)
library(ggplot2)
library(readr)
library(knitr)

df <- read_csv("../data/sample_data.csv")

summary_tab <- df |>
  summarise(total_people = sum(n_people),
           total_consultations = sum(n_consultations),
           avg_consultations_per_ppl = round(total_consultations / total_people, 2)
  )

kable(summary_tab)

```

```{r summary_provider, echo=FALSE, message=FALSE, warning=FALSE}


summary_provider <- df |>
  group_by(provider_type) |>
  summarise(total_consultations = sum(n_consultations),
           .groups = "drop")

ggplot(summary_provider,
       aes(x = provider_type,
           y = total_consultations)
       ) +
  geom_col() +
  labs(title = "Total consultations by provider type",
       x = "Provider type",
       y = "Total consultations")

```

The results show that Allied Health services account for the highest consultation volume. Differences across provider types suggest variation in service demand and delivery patterns. These insights may support resource allocation and service planning decisions.